% !TEX program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Ju Li}

% PDF settings and properties.
\hypersetup{
pdfauthor={\CVAuthor},
%pdfcreator={XeLaTeX},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{Alph} % for keeping hyperref happy
\pagestyle{empty}
\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
19 Follen St, Apt 2, Boston, MA
\par
\href{mailto:ju.li@outlook.com}
{ju.li@outlook.com}
\,\SubBulletSymbol\,
+1\,(617)\,869-0884
\par 
\href{https://www.linkedin.com/in/juli2/}{https://www.linkedin.com/in/juli2/}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExp}

\href{https://krinu.com/}
{\textbf{Krinu}},
Boston, MA
\GapNoBreak
Product Strategy and Development Lead
\hfill
Jul 2020 -- Present
\begin{flushleft}

\BulletItem Led development of Krinu, a sales enablement tool that connects messaging apps such as WhatsApp, Telegram, and iMessage to Customer Relationship Management (CRM) systems such as Hubspot and Salesforce. 

\vspace{0.3em} \SubBulletItem 
Identified ideal customer profile and key painpoints by conducting over 200 customer interviews.  

\vspace{0.3em} \SubBulletItem Designed unified platform for integrating with CRMs and messaging apps. Researched each systems' technical specifications to identify incompatibilities. Designed workarounds to the incompatibilities to deliver consistent feature set across all integrations. 

\vspace{0.75em}
\BulletItem Raised \$150k USD from pre-seed VCs. Developed pitch deck and financial projections using customer and product data extracted from internal SQL databases. 

\end{flushleft}


\href{http://www.everquote.com/}
{\textbf{EverQuote}},
Cambridge, MA
\GapNoBreak
Manager, Strategy and Operations
\hfill
May 2018 -- Jun 2020
\begin{flushleft}

\BulletItem Led go-to-market of multiple new products that contributed 30\% of EverQuote's revenues in 2020.
\vspace{0.5em} \SubBulletItem Secured C-Suite buy-in to designate projects as P1 by presenting highly detailed project plans and projections. Projections highlighted projects' potential impact on revenues and were developed by extracting and analyzing internal SQL data.

\vspace{0.5em} \SubBulletItem Delivered projects on time through careful negotiation of timelines with product, sales, support and marketing teams. Mediated and resolved conflicts and blockers. 

\vspace{0.5em} \SubBulletItem Designed in-depth customized dashboards in Looker and Tableau that enabled leadership and individual contributors to track progress to goals. 

\vspace{0.75em}
\BulletItem Hired, trained, and managed the team's interns. 

\vspace{0.5em} \SubBulletItem Directed multiple high-impact intern projects that were deployed to production, such as an automated system for generating customer performance reports.

\vspace{0.5em} \SubBulletItem Designed onboarding curriculum and playbook that enabled new interns to contribute within 2 weeks. 

\end{flushleft}

\vspace{0.75em}
\href{http://www.analysisgroup.com/}
{\textbf{Analysis Group}},
Boston, MA
\GapNoBreak
Senior Analyst,
Economics Consulting
\hfill
Sep 2014 --
Apr 2018
\begin{flushleft}

\BulletItem Led and mentored team of Analysts in data cleaning, data analysis, and writing of expert reports. Evidence presented in the expert reports helped clients win multiple billion-dollar litigation cases.

\end{flushleft}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{https://www.utoronto.ca/}
{\textbf{University of Toronto}}

\GapNoBreak
\BulletItem
Honours Bachelor of Science (B.Sc.) in Mathematics and Economics (GPA: 3.88 / 4.00)
\hfill
2009 -- 2014

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

English (Fluent), Mandarin Chinese (Intermediate)

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Excel, Databases (MySQL, PostgreSQL, BigQuery), Business Intelligence Tools (Looker, Tableau), CRMs (Salesforce, Hubspot), Programming Languages (VBA, Python, Javascript), Statistical Tools (Stata, SAS, R)

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Poker, musicals, making dumplings, stand-up comedy

\end{body}

\end{document}