% !TEX program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Ju Li}

% PDF settings and properties.
\hypersetup{
pdfauthor={\CVAuthor},
%pdfcreator={XeLaTeX},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{Alph} % for keeping hyperref happy
\pagestyle{empty}
\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
69M Jalan Lim Tai See, Singapore 268475
\par
\href{mailto:ju.li@outlook.com}
{ju.li@outlook.com}
\,\SubBulletSymbol\,
+65\,8011\,2591
\par 
\href{https://www.linkedin.com/in/juli2/}{https://www.linkedin.com/in/juli2/}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExp}

\href{https://krinu.com/}
{\textbf{Krinu}},
Boston, MA
\GapNoBreak
Product Strategy and Development Lead
\hfill
Jul 2020 -- Present
\begin{flushleft}

\BulletItem Led development of a sales enablement tool that connects messaging apps such as WhatsApp, Telegram, and iMessage to Customer Relationship Management (CRM) systems such as Hubspot and Salesforce. 

\vspace{0.3em} \SubBulletItem Interviewed 200+ customers to identify ideal customer profile and their key painpoints. 

\vspace{0.3em} \SubBulletItem Researched technical specifications and managed software development by interns and contractors.

\vspace{0.75em}
\BulletItem Developed business pitch decks, summarizing go-to-market strategy, opportunity size, and competitive analyses. Pitched to hundreds of VC and successfully raised \$150k USD from US and EU pre-seed funds. 

\end{flushleft}


\href{http://www.everquote.com/}
{\textbf{EverQuote}},
Cambridge, MA
\GapNoBreak
Manager, Strategy and Operations
\hfill
May 2018 -- Jun 2020
\begin{flushleft}

\BulletItem Strategic project leader
\vspace{0.5em} \SubBulletItem Led go-to-market of EverQuote's new third-party marketplace product, multi-vertical bundled product, and telemarketing product. Coordinated pre and post launch efforts of sales, customer success and marketing teams to ensure timely execution and maximum realized revenues. Designed in-depth customized dashboards to enable leadership and individual contributors to monitor their/their team's contribution to launch successes. Launched products contributed 30\% of EverQuote's revenues in 2020.

\vspace{0.5em} \SubBulletItem Led redesign and overhaul of B2B organization's sales and customer success commission models, transitioning from a per-unit-sold to a revenue-based commission model. Designed visualization, tracking and reporting tools to enable the sales and customer success teams to be successful under their new commission plans. Resulted in 200\%+ increase in Sales productivity and 60\% growth in revenue between 2019 and 2020.

\vspace{0.75em}
\BulletItem Leadership and mentoring

\vspace{0.5em} \SubBulletItem Designed the team's intern and co-op hiring program. Hired and rapidly brought up to speed the team's intern/co-op/junior hires. Significantly grew team's operational capacity without adding to opex. Team did not add to headcount but effectively supported Sales and Customer Success organizations that had doubled in size.

\end{flushleft}

\vspace{0.75em}
\href{http://www.analysisgroup.com/}
{\textbf{Analysis Group}},
Boston, MA
\GapNoBreak
Senior Analyst,
Economics Consulting
\hfill
Sep 2014 --
Apr 2018
\begin{flushleft}

\BulletItem Led and mentored team of Analysts in data cleaning, data analysis, and writing of expert reports. Evidence presented in the expert reports helped clients win multiple billion-dollar litigation cases.

\end{flushleft}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{https://www.utoronto.ca/}
{\textbf{University of Toronto}}

\GapNoBreak
\BulletItem
Honours Bachelor of Science (B.Sc.) in Mathematics and Economics (GPA: 3.88 / 4.00)
\hfill
2009 -- 2014

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

English (Fluent), Mandarin Chinese (Intermediate)

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Excel, Statistical Tools (Stata, SAS, R), Programming Languages (VBA, Python, Javascript), Databases (MySQL, PostgreSQL, DynamoDB), CRMs (Salesforce, Hubspot), Dashboarding Tools (Looker, Tableau)

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Poker, musicals, collecting old vinyl records, stand-up comedy

\section
{Nationality}
{Nationality}
{PDF:Nationality}

Singapore Citizen 

\end{body}

\end{document}

