% !TEX program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Ju Li}

% PDF settings and properties.
\hypersetup{
pdfauthor={\CVAuthor},
%pdfcreator={XeLaTeX},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{Alph} % for keeping hyperref happy
\pagestyle{empty}
\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
Boston, MA
\par
\href{mailto:ju.li@outlook.com}
{ju.li@outlook.com}
\,\SubBulletSymbol\,
+1\,(617)\,869-0884
\par 
\href{https://www.linkedin.com/in/juli2/}{https://www.linkedin.com/in/juli2/}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExp}

\href{https://krinu.com/}
{\textbf{Krinu}},
Boston, MA
\GapNoBreak
CPO, Co-founder
\hfill
2020 -- Present
\begin{flushleft}

Krinu is a B2B sales enablement tool built around messaging apps like WhatsApp and iMessage. Pivoted from \href{https://getbuylo.com/}
{GetBuyLo}, a B2C travel startup.

\vspace{0.75em}
\BulletItem Strategic leader
\vspace{0.5em} \SubBulletItem Pitched startups to top VCs, adjusting pitch based on visual and verbal feedback. Raised \$150k USD from US and EU startup accelerators.

\vspace{0.5em} \SubBulletItem Pitched product to customers and led product pivots based on user feedback. Led team of 6 interns and contractors to develop new features to address evolving customer needs. 

\vspace{0.75em}
\BulletItem Technical leader
\vspace{0.5em} \SubBulletItem Test test

\vspace{0.5em} \SubBulletItem Led go-to-market of EverQuote's new third-party marketplace product, multi-vertical bundled product, and telemarketing product. Coordinated pre and post launch efforts of sales, customer success and marketing teams to ensure timely execution and maximum realized revenues. Designed in-depth customized dashboards to enable leadership and individual contributors to monitor their/their team's contribution to launch successes. Launched products contributed 30\% of EverQuote's revenues in 2020.

\end{flushleft}

\href{https://antler.co/}
{\textbf{Antler}},
Singapore
\GapNoBreak
Entrepreneur, Startup Incubator Program
\hfill
2021 -- Present
\begin{flushleft}

\BulletItem Rapidly tested 10+ startup ideas with over 300 potential customers over 11 week program to find problem-solution fit. Interviewees ranged from consumers to executives at large enterprises. Spent \$0 on sourcing interviews.

\end{flushleft}

\href{https://getbuylo.com/}
{\textbf{GetBuyLo.com}},
Boston, MA
\GapNoBreak
Product Lead, Co-founder
\hfill
2020 -- Present
\begin{flushleft}

\BulletItem Led team of 4 co-founders + 8 interns \& contractors to build and launch initial product, which was a flight deal newsletter + automated trip planner. Scaled product to 17k subscribers in 6 months. Interviewed with top accelerator YCombinator.

\vspace{0.5em} \BulletItem Pivoted and led development of a flight deal browser extension. Developed and launched in 3 weeks, growing to 500+ installs in 2 months. Interviewed with accelerators YCombinator and Pear.

\end{flushleft}


\href{http://www.everquote.com/}
{\textbf{EverQuote}},
Cambridge, MA
\GapNoBreak
Manager, Strategy and Operations
\hfill
2018 -- 2020
\begin{flushleft}

\BulletItem Strategic project leader
\vspace{0.5em} \SubBulletItem Led go-to-market of EverQuote's new third-party marketplace product, multi-vertical bundled product, and telemarketing product. Coordinated pre and post launch efforts of sales, customer success and marketing teams to ensure timely execution and maximum realized revenues. Designed in-depth customized dashboards to enable leadership and individual contributors to monitor their/their team's contribution to launch successes. Launched products contributed 30\% of EverQuote's revenues in 2020.

\vspace{0.5em} \SubBulletItem Led redesign and overhaul of B2B organization's sales and customer success commission models, transitioning from a per-unit-sold to a revenue-based commission model. Designed visualization, tracking and reporting tools to enable the sales and customer success teams to be successful under their new commission plans. Resulted in 200\%+ increase in Sales productivity and 60\% growth in revenue between 2019 and 2020.

\vspace{0.75em}
\BulletItem Leadership and mentoring

\vspace{0.5em} \SubBulletItem Designed the team's intern and co-op hiring program. Hired and rapidly brought up to speed the team's intern/co-op/junior hires. Significantly grew team's operational capacity without adding to opex. Team did not add to headcount but effectively supported Sales and Customer Success organizations that had doubled in size.

\end{flushleft}

\vspace{0.75em}
\href{http://www.analysisgroup.com/}
{\textbf{Analysis Group}},
Boston, MA
\GapNoBreak
Senior Analyst,
Economics Consulting
\hfill
2014 --
2018
%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{https://www.utoronto.ca/}
{\textbf{University of Toronto}}

\GapNoBreak
\BulletItem
Honours Bachelor of Science (B.Sc.) in Mathematics and Economics (GPA: 3.88 / 4.00)
\hfill
2009 -- 2014

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

English (Fluent), Mandarin Chinese (Intermediate)

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Excel, Bloomberg, CapitalIQ, Statistical Tools (Stata, SAS, R), Programming Languages (VBA, Python, Javascript), Databases (MySQL, PostgreSQL, DynamoDB), CRM (Salesforce, Hubspot), Dashboarding Tools (Looker, Tableau)

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Poker, musicals, recreating Singaporean dishes, collecting old vinyl records, stand-up comedy

\end{body}

\end{document}
\vspace{0.5em} \SubBulletItem Developed an algorithm for computing product inventory, synthesizing data from disparate sources into a simple to understand metric. Automated computation utilizing Python scripts. Created dashboards and visualizations in Looker, enabling Leadership to easily understand inventory trends and pivot organization towards undersold territories.

