% !TEX program = xelatex
% !TEX encoding = UTF-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}
\usepackage{xeCJK}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Ju Li}

% PDF settings and properties.
\hypersetup{
pdfauthor={\CVAuthor},
%pdfcreator={XeLaTeX},
pdfkeywords={},
pdfpagemode={},
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagenumbering{Alph} % for keeping hyperref happy
\pagestyle{empty}
\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\vspace{1em}
244 St Pauls Ave, Apt 621, Jersey City, NJ 07306
\par
\href{mailto:ju.li@outlook.com}{ju.li@outlook.com}
\,\SubBulletSymbol\,
\href{tel:16178690884}{+1\,(617)\,869\,0884}
\par 
\href{https://www.linkedin.com/in/juli2/}{https://www.linkedin.com/in/juli2/}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work\newline
Experience}
{Work Experience}
{PDF:WorkExp}

\href{https://www.masterworks.com/}
{\textbf{Masterworks}},
New York, NY
\GapNoBreak
Membership Operations Manager
\hfill
Mar 2023 -- Present
\begin{flushleft}

\BulletItem Sole developer of special projects such as AI intro videos and custom telephony integrations to test new strategies that improved member activation rates by 18\% and member investments by 29\%. 

\vspace{0.3em} \BulletItem Conducted technical research into various solutions. Negotiated with vendors. Documented limitations. Strategized workarounds. Designed no-code workflows and wrote custom Python/Typescript functions to execute projects. Enabled sales team to start new tests in days, not weeks.

\end{flushleft}

\textbf{Various Startups},
Boston, MA
\GapNoBreak
Cofounder, CPO of \href{https://krinu.com/}{\textbf{Krinu.com}}
\hfill
Jul 2021 -- Jan 2023
\GapNoBreak
Founder of \href{https://tripli.com/}{\textbf{Tripli.com}} and \href{https://getbuylo.com/}{\textbf{GetBuyLo.com}}
\hfill
Jul 2020 -- Jun 2021
\begin{flushleft}

\BulletItem Managed 5+ contractors and interns in the development of:

\vspace{0.3em} \SubBulletItem Krinu - a sales enablement tool connecting messaging apps like WhatsApp and Telegram with customer relationship management systems like Hubspot and Salesforce

\vspace{0.3em} \SubBulletItem GetBuyLo - a browser extension that finds cheap flights at checkout

\vspace{0.3em} \SubBulletItem Tripli - an automated trip planning tool

\vspace{0.3em}
\BulletItem Raised \$150k USD from pre-seed VCs. Developed pitch deck and financial projections using customer and product data extracted from internal SQL databases. 

\end{flushleft}

\href{https://www.everquote.com/}
{\textbf{EverQuote}},
Cambridge, MA
\GapNoBreak
Manager, Strategy and Operations
\hfill
May 2018 -- Jun 2020
\begin{flushleft}


\BulletItem Led re-organization of B2B organization's sales and customer success teams. Completely revamped the hiring, commission, and operational strategy that resulted in 100\%+ increase in Sales productivity and 60\% growth in revenue between 2019 and 2020.

\vspace{0.4em} \SubBulletItem 	Negotiated and oversaw optimization of commission models, transitioning the teams from a per-unit-sold to a revenue-based commission model. 

\vspace{0.4em} \SubBulletItem 	Designed visualization, tracking and reporting tools to enable individual contributors and managers to succeed under the new commission plans. 

\vspace{0.4em} \SubBulletItem 	Developed Unit Economics Model for each B2B territory. This model quantified the performance and opportunity for growth for each B2B territory, laying the groundwork for EverQuote's B2B re-organization and growth in 2020.

\end{flushleft}

\href{https://www.analysisgroup.com/}
{\textbf{Analysis Group}},
Boston, MA
\GapNoBreak
Senior Analyst,
Economics Consulting
\hfill
Sep 2014 --
Apr 2018
\begin{flushleft}

\BulletItem Led and mentored team of Analysts in data cleaning, data analysis, and writing of expert reports. Evidence presented in the expert reports helped clients win multiple billion-dollar litigation cases.

\end{flushleft}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{https://www.utoronto.ca/}
{\textbf{University of Toronto}}

\GapNoBreak
\BulletItem
Honours Bachelor of Science (B.Sc.) in Mathematics and Economics (GPA: 3.88 / 4.00)
\hfill
2009 -- 2014

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section
{Languages}
{Languages}
{PDF:Languages}

English (Fluent), Mandarin Chinese (Intermediate)

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}

Excel, Databases (MySQL, PostgreSQL, BigQuery), Business Intelligence Tools (Looker, Tableau), CRMs (Salesforce, Hubspot), Programming Languages (VBA, Python, Javascript), Statistical Tools (Stata, SAS, R)

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section
{Interests}
{Interests}
{PDF:Interests}

Poker, musicals, making dumplings, stand-up comedy

\end{body}

\end{document}